Bare Demo of IEEEtran.cls\\ for IEEE Conferences

### 2016-12-01 paper.tex
Anonymizing

\subsubsection{Capturing the Keystroke and Mouse Data} 
While a student is trying
to solve an exercise, a script coded in JavaScript is running in the background,
which captures every keystroke, mouse movement and mouse button press. Each
capture of these events records a timestamp in milliseconds (using the method
getTime() of Javascript's built-in class Date) that describes when the event
occurred. If the event is a keystroke, the script captures what key was
specifically pressed, and what type of event occurred, it can be either a key-
down or a key-up event. If it is an event related to a mouse button press, the
key code of that button is recorded, as well as the type of event occurred again
key-down or key-up. Finally, if the event was a mouse movement, the mouse
coordinates inside of the web browser are recorded. The script monitors the
mouse position every 100 milliseconds, and only if the position has changed, it
records the new position. Each time a learner tries to evaluate a program, all
the data generated is sent to the server along with the code. When the result of
the execution is returned, all records are cleared and the process starts again.
There is no problem if the user leaves for a long period of time, because no
event will be triggered. If a user copies and then pastes the code from another
source, this will be recorded. There is a limitation, only the browser-editor
must be used; this could be a problem for more advanced programmers needing
specialized editors.  On the other hand a browser-based editor with the
corresponding remote execution, does not require the installation of
interpreters or compilers in learner’s computer. The code could even be written
in a mobile device or any web-enabled device.  The interface of the web-based
editor is shown in Figure \ref{fig_editor}. Programming exercises are evaluated using unit
tests; the results of the evaluation are shown to users. If all tests the
program is considered to be correct. An example execution is shown in the left
side image of Figure \ref{fig_editor}. In this example the learner was asked to write a
function to add two numbers, in Python. The source code for the Protoboard web
based learning environment including the KD and MD functions are open source and
available as Github repositories at http://git.io/vJlUV also the code for the
sandbox is in http://git.io/vJlUj. % Anonimyze this, I guess - JJ

@@

To calculate the average and standard deviations of these key presses, the delays
between a key-down and a key-up event of the left button clicks are used. In
addition to these averages and standard deviations of the delays between
keystrokes and mouse button presses, the average and standard deviations of the
number of total events contained in a digraph and a trigraph are calculated.
These features are proposed and explained by Epp, Lippold y Mandryk \cite{epp2011identifying}. Most
of the times, a digraph should contain four events, while a trigraph six.
However, sometimes an individual can start a digraph or a trigraph before ending
the previous one. These additional features represent these particular cases,
and could be meaningful for the estimation of a learner's affective states.
Regarding the mouse movements, the average and standard deviation of the
duration of each mouse movement, and the averages and standard deviations of the
movements in the axes X and Y are also calculated. Lastly, a final feature is
added to preprocessing of the data. The web tutorial recorded how many attempts
a student required before successfully solving an exercise. This number of
attempts is also included in the feature vector. The final feature vector
consists of 39 features; these are based on the work of Epp, Lippold \& Mandryk
\cite{epp2011identifying} and are shown in Table 1. (The code used for this step is available at:
https://github.com/amherag/keyboard-mouse-dynamics). %anonymize

@@

%Start with a reference to the Table (and check numbering) - JJ
The results obtained with this method are satisfactory, considering a free-text
was used. % don't get this. What free text? A program? - JJ
The accuracies and kappa coefficients obtained are close to what is
usually obtained in fixed-text methods, for example, the results presented in
Epp, Lippold y Mandryk (2007). %A reference!!! - JJ
 In the case of the kappa coefficients, it is
usual to see values below 0.2 in methods involving free-text. In this case, some
values of kappa were close to 0.5, is important to consider the values of kappa
in these results because the class distribution is not uniformly distributed. As
it is observed in many works in affective recognition, decision trees normally
produce competitive accuracy. In this case the J-48 classifier obtained an
accuracy of 80.48\%, which is marginally better than the others, and an accepted kappa
statistic for the kind of problem. The artificial neural network % Which one? - JJ
give the highest
accuracy in the classification of frustration.

@@

% use section* for acknowledgment 
\section*{Acknowledgment} 
This received funding from Tecnólogico Nacional de México through the project: Técnicas de
computación inteligente para el secuenciado adaptativo de ejercicios de
programación en la nube.

>>>>

\subsubsection{Capturing the Keystroke and Mouse Data} 
While a student is trying
to solve an exercise, a script coded in JavaScript is running in the background,
which captures every keystroke, mouse movement and mouse button press. Each
capture of these events records a timestamp in milliseconds (using the method
getTime() of Javascript's built-in class Date) that describes when the event
occurred. If the event is a keystroke, the script captures what key was
specifically pressed, and what type of event occurred, it can be either a key-
down or a key-up event. If it is an event related to a mouse button press, the
key code of that button is recorded, as well as the type of event occurred again
key-down or key-up. Finally, if the event was a mouse movement, the mouse
coordinates inside of the web browser are recorded. The script monitors the
mouse position every 100 milliseconds, and only if the position has changed, it
records the new position. Each time a learner tries to evaluate a program, all
the data generated is sent to the server along with the code. When the result of
the execution is returned, all records are cleared and the process starts again.
There is no problem if the user leaves for a long period of time, because no
event will be triggered. If a user copies and then pastes the code from another
source, this will be recorded. There is a limitation, only the browser-editor
must be used; this could be a problem for more advanced programmers needing
specialized editors.  On the other hand a browser-based editor with the
corresponding remote execution, does not require the installation of
interpreters or compilers in learner’s computer. The code could even be written
in a mobile device or any web-enabled device.  The interface of the web-based
editor is shown in Figure \ref{fig_editor}. Programming exercises are evaluated using unit
tests; the results of the evaluation are shown to users. If all tests the
program is considered to be correct. An example execution is shown in the left
side image of Figure \ref{fig_editor}. In this example the learner was asked to write a
function to add two numbers, in Python. The source code for the Protoboard web
based learning environment including the KD and MD functions are open source and
available as Github repositories at http://--------.--/----- also the code for the
sandbox is in http://--------.--/-----. % Anonimyze this, I guess - JJ

@@

To calculate the average and standard deviations of these key presses, the delays
between a key-down and a key-up event of the left button clicks are used. In
addition to these averages and standard deviations of the delays between
keystrokes and mouse button presses, the average and standard deviations of the
number of total events contained in a digraph and a trigraph are calculated.
These features are proposed and explained by Epp, Lippold y Mandryk \cite{epp2011identifying}. Most
of the times, a digraph should contain four events, while a trigraph six.
However, sometimes an individual can start a digraph or a trigraph before ending
the previous one. These additional features represent these particular cases,
and could be meaningful for the estimation of a learner's affective states.
Regarding the mouse movements, the average and standard deviation of the
duration of each mouse movement, and the averages and standard deviations of the
movements in the axes X and Y are also calculated. Lastly, a final feature is
added to preprocessing of the data. The web tutorial recorded how many attempts
a student required before successfully solving an exercise. This number of
attempts is also included in the feature vector. The final feature vector
consists of 39 features; these are based on the work of Epp, Lippold \& Mandryk
\cite{epp2011identifying} and are shown in Table 1. (The code used for this step is available at:
https://------.---/-------/-----------------------). %anonymize

@@

%Start with a reference to the Table (and check numbering) - JJ
The results obtained with this method are satisfactory, considering a free-text
was used. % don't get this. What free text? A program? - JJ
The accuracies and kappa coefficients obtained are close to what is
usually obtained in fixed-text methods, for example, the results presented in
Epp, Lippold y Mandryk \cite{epp2011identifying}. %A reference!!! - JJ  
												 %Added	
 In the case of the kappa coefficients, it is
usual to see values below 0.2 in methods involving free-text. In this case, some
values of kappa were close to 0.5, is important to consider the values of kappa
in these results because the class distribution is not uniformly distributed. As
it is observed in many works in affective recognition, decision trees normally
produce competitive accuracy. In this case the J-48 classifier obtained an
accuracy of 80.48\%, which is marginally better than the others, and an accepted kappa
statistic for the kind of problem. The artificial neural network % Which one? - JJ
give the highest
accuracy in the classification of frustration.

@@

% use section* for acknowledgment 
\section*{Acknowledgment} This work received funding from some places, but this is 
only to keep the space neeed. this is only to keep the space neeed. this is  only to 
keep the space neeed. only to keep the space neeed. this is only to keep the space neeed. 
this is  only to only to keep the space neeed. this is only to keep the space neeed. 
this is  only to  keep the space neeed. only to keep the space neeed. this is only to
this is  only to
